\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-16 experimental_results.tex
missing bracket
final changes by daniela to manuscript

\subsection{Aggregate System}
\label{sec:aggregate_system}
The aggregate \dr{soft manipulation} system is shown in Figure~\ref{fig:sys_overview}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:sys_overview}
\end{centering}
\end{figure}

@@

\subsection{Repeated Grasp Experiments}
We performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

\subsection{Experimental Insights and Limitations}
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
%Most of the payload capability is already used up by the attached gripper itself.
%A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
%The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
%\rkk{The gripper presented did not only pick up round objects, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
%Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment. 
%, around half the length of the gripper. 
%A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
%\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}

>>>>

\subsection{Experimental Platform}
The \dr{soft manipulation} system is shown in Figure~\ref{fig:experimental_platform}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:experimental_platform}
\end{centering}
\end{figure}

@@

\subsection{Grasp Experiments}
\rkk{Using the experimental platform in Figure~\ref{fig:experimental_platform}, we implemented the planning algorithm described in Section~\ref{sec:processing_and_control}.
We evaluated the manipulator system for repeatability and ability to handle uncertainty.
The experiments consisted of picking and placing several objects of unknown geometry placed at an unknown location.
We measured the execution time and captured the location data during the experiments.
Specifically,}
we performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

@@

\subsection{Experimental Insights and Limitations}
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
%Most of the payload capability is already used up by the attached gripper itself.
%A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
%The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
%\rkk{The gripper presented did not only pick up round objects, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
%Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment.}
%, around half the length of the gripper. 
%A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
%\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}

### 2015-10-16 introduction.tex
final changes by daniela to manuscript

Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects \dr{of unknown geometry}. 
%By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient};

@@

\subsection{Contributions}
We take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
Our work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system.} 
\dr{Our planning and control method successfully copes with uncertainties in the object geometries, object placement and manipulator modeling.}
%We do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, 
We provide in this work the following contribution to soft robotics:
\begin{itemize}
  \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
  \item \rkk{Proper autonomous manipulation of various objects} \dr{of unknown geometry placed randomly in the working space of a soft manipulator} \rkk{without requiring force sensing or accurate positioning.} 
   \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
  %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
%\item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
\end{itemize}

>>>>

Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects \dr{of unknown geometry}. 
%By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient}; 
\rkk{In this paper we describe a planar soft robot manipulator we developed toward this goal.
We focus on the design, fabrication, control, and planning aspects of this soft robot.}

@@

\subsection{Contributions}
We take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
Our work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system.} 
\dr{Our planning and control method successfully copes with uncertainties in the object geometries, object placement and manipulator modeling.}
%We do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, 
We provide in this work the following contribution to soft robotics:
\begin{itemize}
  \item The design and fabrication process of a soft 2D manipulator.
  \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
  \item \rkk{Autonomous manipulation experiments with various objects} \dr{of unknown geometry placed randomly in the working space of a soft manipulator} \rkk{without requiring force sensing or accurate positioning.} 
   \item Data from repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
  %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
%\item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
\end{itemize}

### 2015-10-16 processing_control.tex
final changes by daniela to manuscript

\subsection{Grasp Object Planner}
\label{subsec:grasp_planner}
A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a cylinder enclosing the object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations called approach configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1.. numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.

@@

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
\rkk{The weights are set by the matrix $\mathbf{R}$.}
\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience. 
\rkk{The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace. That occurs if the object was user-placed outside the workspace. Before performing the optimization, a feasability check is performed using the arm's forward kinematics.}

>>>>

\subsection{Grasp Object Planner}
\label{subsec:grasp_planner}
The grasp-and-place system plans a feasible approach motion to the object.
That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a cylinder enclosing the object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations called approach configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1.. numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.

@@

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
\rkk{The weights are set by the matrix $\mathbf{R}$.}
\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience. 
\rkk{The optimization becomes over-constrained only if it has to find an arm pose outside of the arm's reachable workspace. That occurs if the object was user-placed outside the workspace. Before performing the optimization, a feasability check is performed using the arm's forward kinematics.}
